Non-target Analysis for Wastewater Treatment Evaluation

### 2025-05-03 dev/demo_nts.Rmd
Small fix to RamanAnalyses and Quantification

---
title: 'Non-target Screening (NonTargetAnalysisResults) Wastewater Treatment Evaluation'
author:
  name: Ricardo Cunha
  email: cunha@iuta.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    fig_caption: true
    toc: true
    number_sections: true
    toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{'Non-target Screening (NonTargetAnalysisResults) Wastewater Treatment Evaluation'}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

The showcase will use the StreamFind *MassSpecEngine*, which encapsulates all tools required for parsing, storing, processing and visualizing MS data. Note that not all methods/functions will be shown as the demonstration focuses of the workflow to assess wastewater ozonation. Other processing methods are available in the StreamFind package and can be found in the [StreamFind reference documentation](https://odea-project.github.io/StreamFind/reference/index.html).

>>>>

---
title: 'Non-target Analysis for Wastewater Treatment Evaluation'
author:
  name: Ricardo Cunha
  email: cunha@iuta.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    fig_caption: true
    toc: true
    number_sections: true
    toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{'Non-target Analysis for Wastewater Treatment Evaluation'}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

The showcase will use the StreamFind *MassSpecEngine*, which encapsulates all tools required for parsing, storing, processing and visualizing MS data. Note that not all methods/functions will be shown, as the demonstration focuses of the workflow to assess wastewater treatment. Other processing methods for MS data are available in the StreamFind package and can be found in the [StreamFind reference documentation](https://odea-project.github.io/StreamFind/reference/index.html).
